Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
finished changes to the evaluation and discussion

\paragraph{Metric}
We measure quality software contributions by based on the build status of the
commit: if the build passes or fails.
To determine which factors are important for predicting build success, we used
a decision tree classifier, because decision tress are well a tested supervised 
classifier that are easy to interpret.
To explore the question of technical and social factors, we first build a
decision tree classifier using only the technical factors.  This first model
allowed us to understand how well commit complexity estimated build integration
success.  We then added the social factors to understand how the social factors
integrated with the technical factors when predicting build integration success.
We evaluated the predictive power of these two 
models with 10-fold cross validation.
\section{Building Dataset}
\label{approach}

@@

\hline
\end{tabular}
\\
\center
	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
    cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column). 
	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
	%Zack: the above sentence isn't true for the second row.
	}   
\end{table*}

We evaluated the predictive power of the social factors using a decision
tree~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. The decision trees were evaluated using 10-fold cross 
validation with the data in each data set.
To give an answer to main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?", we 
present the following results:

@@

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm, first without downsampling. The 
decision tree built from
only the technical indicators has a correct classification rate of 77.01\% which
means the technical attributes only increased the prediction accuracy by about 3\%.
Adding the social data increased the classifier's accuracy from 77.01\% to
81.10\%, a 4.09\% increase.

On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, when predicting a successful build in
all instances would produce 50.00\% accuracy.  After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
social data can be used to improve predictions of build integration success.

@@

To determine if core team member's have greater build success rates,
we classified the build success rate for
core team members and non-core team members in the data set without 
downsampling.  We found that core team members
triggered of 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.  This shows that core team members are more
likely to have a successful build integration than non-core team members.

@@

We also investigated if developers with followers were more likely to have a
successful build integration, since have followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build in the data set without 
downsampling.  We found that only 0.87\% of the
contributions in the data set was performed by developers with zero 
followers (excluding the developers in which we were not able to extract profile
information for). We found that 99.13\% of the contributions were performed by
developers with at least one or more followers.
We found that developers with 0 followers had a successful build commit 68.49\%
of the time.  Developers with one or more followers were successful 74.78\% of
the time.

>>>>

\paragraph{Metric}
We measure quality software contributions by based on the build status of the
commit: if the build passes or fails.
To determine which factors are important for predicting build success, we used
a decision tree classifier~\cite{Quinlan86}, because decision tress are well a 
tested supervised classifier that are easy to interpret.
To explore the question of technical and social factors, we first build a
decision tree classifier using only the technical factors.  This first model
allowed us to understand how well commit complexity estimated build integration
success.  We then added the social factors to understand how the social factors
integrated with the technical factors when predicting build integration success.
We evaluated the predictive power of these two 
models with 10-fold cross validation.
\section{Building Dataset}
\label{approach}

@@

\hline
\end{tabular}
\\
\center
	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
    cross validation of two decision trees with a non-downsampled dataset (2nd and 3rd column) and downsampled (4th and 5th column). 
	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
	%Zack: the above sentence isn't true for the second row.
	}   
\end{table*}
To give an address to main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?", we 
created a decision tree classifier~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. The decision trees were evaluated using 10-fold cross 
validation with the data in each data set.

@@

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm, first without downsampling. The 
decision tree built from
only the technical indicators has a correct classification rate of 77.01\% which
means the technical attributes only increased the prediction accuracy by about 3\%
compared to a base line rate of guessing the build passed in all cases.
Adding the social data increased the classifier's accuracy from 77.01\% to
81.10\%, a 4.09\% increase.

On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
 After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

@@

To determine if core team member's have greater build success rates,
we classified the build success rate for
core team members and non-core team members in the data set without 
downsampling.  We found that core team members
triggered 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.  This shows that core team members are more
likely to have a successful build integration than non-core team members.

@@

We also investigated if developers with followers were more likely to have a
successful build integration, since have followers may be seen as vouching for
the developer's abilities.  We specifically investigated if a developer with 
followers was more likely to pass the build in the data set without 
downsampling.  We found that only 0.87\% of the
contributions in the data set was performed by developers with zero 
followers (excluding the developers in which we were not able to extract profile
information for). We found that 99.13\% of the contributions were performed by
developers with at least one or more followers.
Developers with 0 followers had a successful build commit 68.49\%
of the time.  Developers with one or more followers were successful 74.78\% of
the time.
